### 2022-05-30 chapters/04-chapter-4.tex
txs auto checkin

\subsubsection{Kasus SI3}
Dari gambar \ref{result_cpu_2} dan \ref{result_mem_2} terlihat bahwa \textit{engine} menggunakan \textit{resource} CPU sebanyak 0.057 \textit{core} dan Memory sebanyak 128.71 MiB.

>>>>

\subsubsection{Kasus SI3}
Dari gambar \ref{result_cpu_3} dan \ref{result_mem_3} terlihat bahwa \textit{engine} menggunakan \textit{resource} CPU sebanyak 0.057 \textit{core} dan Memory sebanyak 128.71 MiB.
